### 2020-01-04 cv_models.tex
place holders for CV VGG

>>>>

\begin{figure}[t]
    \centering
    \subfigure[ Frobenius Norm ]{
        \includegraphics[width=5cm]{img/vgg-fnorm.png}
        \label{fig:vgg-fnorm}
    }
    \qquad
    \subfigure[ Spectral Norm ]{
        \includegraphics[width=4.9cm]{img/vgg-snorm.png}
        \label{fig:vgg-snorm}
    }
    \qquad
    \subfigure[ Weighted Alpha ]{
        \includegraphics[width=4.9cm]{img/vgg-walpha.png}
        \label{fig:vgg-walpha}
    }
    \qquad
    \subfigure[ Alpha-Norm ]{
        \includegraphics[width=4.9cm]{img/vgg-pnorm.png}
        \label{fig:vgg-pnorm}
    }
    \caption{Comparison of norm metrics vs reported test accuracy for pretrained VGG models, trained on ImageNet, available in pyTorch.  Plots will be updated and replace }

    \label{fig:vgg-metrics}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[scale=0.30]{img/vgg-alpha-layers.png}
  \label{fig:vgg-alpha-layers}
    \caption{Power law exponent $\alpha$ vs layer for VGG11 and VGG19. }
\end{figure}

### 2020-01-04 methods.tex
place holders for CV VGG

section{Methods}
\label{sxn:methods}

@@

\begin{itemize}
 \item Frobenius Norm: $\Vert\mathbf{W}\Vert^{2}_{F}=\Vert\mathbf{W}\Vert^{2}_{2}=\sum_{i,j}w^{2}_{i,j}$
 \item Spectral Norm:  $\Vert\mathbf{W}\Vert_{\infty}=\lambda_{max}$
 \item $\alpha-$Norm (or Shatten Norm) $\Vert\mathbf{W}\Vert^{\alpha}_{\alpha}=\sum_{i=1}^{M}\lambda^{\alpha}$,
\end{itemize}

@@

\begin{itemize}
 \item $\hat{\alpha}=\alpha\log\lambda_{max}\approx\log\Vert\mathbf{W}\Vert^{\alpha}_{\alpha}$
\end{itemize}

@@

To verify that our approach is meaningful, we need to see the ESD is neither due to a random matrix, nor due to unsually large matrix elements. We examine typical Conv2D layer for the pretained AlexNet model (distributed with pyTorch).  Figure \ref{fig:alexnet1} displays the ESD for the first slice (or matrix $\mathbf{W}$) of the third Conv2D layer, extracted from a 4-index Tensor of shape $(384, 192, 3, 3)$.  The red line displays the best fit to a random matrix, using the Marchenko pastur theory\cite{MM}.  We can see the random matrix model does not describe the ESD very well. For comparison, Figure \ref{fig:alexnet2} shows the ESD of the same matrix, randomly shuffled; here looks similar to the red line plot of the orginal ESD.  In fact, the empircal ESD is better modeled with a truncated power law distribtion.

Although the ESD is \emph{Heavy Tailed}, this does not imply that the orginal matrix $\mathbf{W}$ is itself heavy tailed--
only the correlation matrix $\mathbf{X}$ is. (i.e. maximum eigenvalue) than the original. If $\mathbf{W}$ was, 
then it would contain 1 or more unusually large matrix elements, and they would dominate the ESD.  
Of course the randomized $\mathbf{W}$ would also be heavy tailed, but its ESD neither resembles the original
nor is it heavy tailed.  So we can rule out $\mathbf{W}$ being heavy tailed.

@@

These plots tell us that the Tensor Slice of the Conv2D contains significant correlations learned from the data.  
By modeling the ESD with a power law distribution $\lambda^{\alpha}$, we can characterize the amount of correlation learned;
the smaller the exponent $\alpha$, the more correlation in the weight matric.

>>>>

\section{Methods}
\label{sxn:methods}

@@

\begin{itemize}
 \item Frobenius Norm: $\Vert\mathbf{W}\Vert^{2}_{F}=\Vert\mathbf{W}\Vert^{2}_{2}=\sum_{i,j}w^{2}_{i,j}$
 \item Spectral Norm:  $\Vert\mathbf{W}\Vert_{\infty}=\lambda_{max}$
 \item $\alpha-$Norm (or Shatten Norm) $\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}=\sum_{i=1}^{M}\lambda^{\alpha}$,
\end{itemize}

@@

\begin{itemize}
 \item $\hat{\alpha}=\alpha\log\lambda_{max}\approx\log\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}$
\end{itemize}

@@

To verify that our approach is meaningful, we need to see the ESD is neither due to a random matrix, nor due to unsually large matrix elements, but, in fact, captures correlations learned from the data.  We examine typical Conv2D layer for the pretained AlexNet model (distributed with pyTorch).  Figure \ref{fig:alexnet1} displays the ESD for the first slice (or matrix $\mathbf{W}$) of the third Conv2D layer, extracted from a 4-index Tensor of shape $(384, 192, 3, 3)$.  The red line displays the best fit to a random matrix, using the Marchenko pastur theory\cite{MM}.  We can see the random matrix model does not describe the ESD very well. For comparison, Figure \ref{fig:alexnet2} shows the ESD of the same matrix, randomly shuffled; here looks similar to the red line plot of the orginal ESD.  In fact, the empircal ESD is better modeled with a truncated power law distribtion.

Although the ESD is \emph{Heavy Tailed}, this does not imply that the orginal matrix $\mathbf{W}$ is itself heavy tailed--
only the correlation matrix $\mathbf{X}$ is. If $\mathbf{W}$ was, 
then it would contain 1 or more unusually large matrix elements, and they would dominate the ESD.  
Of course the randomized $\mathbf{W}$ would also be heavy tailed, but its ESD neither resembles the original
nor is it heavy tailed.  So we can rule out $\mathbf{W}$ being heavy tailed.

@@

These plots tell us that the Tensor Slice of the Conv2D contains significant correlations learned from the data.  
By modeling the ESD with a power law distribution $\lambda^{\alpha}$, we can characterize the amount of correlation learned;
the smaller the exponent $\alpha$, the more correlation in the weight matrix.
